---
title: "p8105_hw1_nec2159"
author: "Nicole Criscuolo"
date: "2025-09-11"
output: github_document
---

## Problem 1
```{r echo = FALSE, message = FALSE}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

The variables in this data set include `r names(early_january_weather)`. The highest and lowest temperatures recorded were `r max(early_january_weather$temp)` and `r min(early_january_weather$temp)`. The average humidity and wind speed were `r mean(early_january_weather$humid)` and `r mean(early_january_weather$wind_speed)`, respectively. 

All the values for temperature are `r unique(early_january_weather$temp)`. 

All the values for wind speed are `r unique(early_january_weather$wind_speed)`.

The number of subjects in the data set is `r nrow(early_january_weather)`, and the number of variables is `r ncol(early_january_weather)`. 

The average temperature recorded is `r mean(early_january_weather$temp)`.

```{r}
temp_plot <- ggplot(early_january_weather, aes (x = time_hour, y = temp, color = humid)) + geom_point()
temp_plot
```
The plot's peaks and valleys show how temperature was changing throughout the hours of each day. The gradual increase from January 1st to January 14 show that the average temperature throughout the day was increasing each day for these two weeks. After January 14, there was a large drop in temperature. The humidity seemed to increase with temperature for the most part as there was the most humidity around January 13 and 14 and the least around January 3.

```{r eval = FALSE}
ggsave("temp_plot.png", plot = temp_plot)
```

## Problem 2

```{r}
example_df = 
  tibble(
    random_samp = rnorm(10),
    greater_0 = random_samp > 0,
    vec_char = c("My", "name", "is", "Nicole", "and", "I", "go", "to", "Columbia", "University"),
    vec_factor = factor(c("good", "good", "good", "alright", "alright", "alright", "alright", "bad", "bad", "bad"))
)

random_samp <- example_df %>% pull(random_samp)
mean(random_samp)

greater_0 <- example_df %>% pull(greater_0)
mean(greater_0)

vec_char <- example_df %>% pull(vec_char) 
mean(vec_char)

vec_factor <- example_df %>% pull(vec_factor)
mean(vec_factor)
```

I am able to take the mean of the random sample variable since this is a numeric variable in addition to the "greater than 0" variable since this is a logical variable. The other two variables are categorical, so I cannot take their means.

```{r eval = FALSE}
greater_0_numeric <- as.numeric(greater_0)
greater_0_numeric

vec_char_numeric <- as.numeric(vec_char)
vec_char_numeric

vec_factor_numeric <- as.numeric(vec_factor)
vec_factor_numeric
```
The logical and factor variables get converted to numbers. This makes sense as these variables have a limited number of possible responses. For example, the factor variable responses of "good," "alright," and "bad," can easily be assigned number values, as can "True" or "False" for the logical variable. This would not make sense to do with the character variables as there are an unlimited number of possible responses. This explains why I was not able to take the mean of the character variable or factor variable. However, I was able to take the mean of the logical greater than 0 variable as they had already been assigned either "1" or "0" based on whether they were "True" or "False.

