---
title: "p8105_hw1_nec2159"
author: "Nicole Criscuolo"
date: "2025-09-11"
output: github_document
---

## Problem 1
```{r}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

The variables in this data set include `r names(early_january_weather)`. The highest and lowest temperatures recorded were `r max(early_january_weather$temp)` and `r min(early_january_weather$temp)`. The average humidity and wind speed were `r mean(early_january_weather$humid)` and `r mean(early_january_weather$wind_speed)`, respectively. 

All the values for temperature are `r early_january_weather$temp`. 

All the values for humidity are `r early_january_weather$humid`.

The number of observations in the data set is `r nrow(early_january_weather)`, and the number of variables is `r ncol(early_january_weather)`. 

The average temperature recorded is `r mean(early_january_weather$temp)`.

```{r}
temp_plot <- ggplot(early_january_weather, aes (x = time_hour, y = temp, color = humid)) + geom_point()
temp_plot
```
The plot's peaks and valleys show how temperature was changing throughout the hours of each day. The gradual increase from January 1st to January 14 show that the average temperature throughout the day was increasing each day for these two weeks. After January 14, there was a large drop in temperature. The humidity seemed to increase with temperature for the most part as there was the most humidity around January 13 and 14 and the least around January 3.
